### 2022-06-18 papers/scp/response-to-reviewers.txt

We have now received reviewers' reports and a recommendation by the
handling editor; based upon the recommendation and the reviews, we
would like to ask you prepare a minor revision taking the comments of
the reviewers into account.

The due date for revision is Feb 14, 2020.  If this deadline is out of
sync with other due dates communicated to you outside EES, then please
contact the handling editor to settle this.

If you decide to revise the work, please submit a list of changes or a
rebuttal against each point which is being raised when you submit the
revised manuscript.

To submit a revision, please go to https://ees.elsevier.com/scico/ and
login as an Author.  Your username is: wadler@inf.ed.ac.uk If you need
to retrieve password details, please go to:
https://ees.elsevier.com/scico/automail_query.asp

@@

METHODSX CO-SUBMISSION (OPTIONAL)

If you have customized (a) research method(s) for the project
presented in your Science of Computer Programming article, you are
invited to submit this part of your work as MethodsX article alongside
your revised research article. MethodsX is an independent journal that
publishes the work you have done to develop research methods to your
specific needs or setting. This is an opportunity to get full credit
for the time and money you may have spent on developing research
methods, and to increase the visibility and impact of your work.

How does it work?  1) Fill in the MethodsX article template:
https://www.elsevier.com/MethodsX-template 2) Place all MethodsX files
(including graphical abstract, figures and other relevant files) into
a .zip file and upload this as a 'Method Details (MethodsX) ' item
alongside your revised Science of Computer Programming
manuscript. Please ensure all of your relevant MethodsX documents are
zipped into a single file.  3) If your Science of Computer Programming
research article is accepted, your MethodsX article will automatically
be transferred to MethodsX, where it will be reviewed and published as
a separate article upon acceptance.  MethodsX is a fully Open Access
journal, the publication fee is only 520 US$.

Questions?  Please contact the MethodsX team at methodsx@elsevier.com.
Example MethodsX articles can be found here:
https://www.sciencedirect.com/science/journal/22150161 Yours sincerely,

@@

INTERACTIVE PLOT VIEWER (OPTIONAL)

Science of Computer Programming features the Interactive Plot Viewer,
see: https://www.elsevier.com/interactiveplots. Interactive Plots
provide easy access to the data behind plots. To include one with your
article, please prepare a .csv file with your plot data and test it
online at
https://authortools.elsevier.com/interactiveplots/verification before
submission as supplementary material.  PLEASE NOTE: Science of
Computer Programming would like to enrich online articles by
displaying interactive figures that help the reader to visualize and
explore your research results. For this purpose, we would like to
invite you to upload figures in the MATLAB .FIG file format as
supplementary material to our online submission system. Elsevier will
generate interactive figures from these files and include them with
the online article on SciVerse ScienceDirect. If you wish, you can
submit .FIG files along with your revised submission.

@@

________________

For further assistance, please visit our customer support site at
https://help.elsevier.com/app/answers/list/p/7923. Here you can search
for solutions on a range of topics, find answers to frequently asked
questions and learn more about EES via interactive tutorials. You will
also find our 24/7 support contact details should you need any further
assistance from one of our customer support representatives.

### 2022-11-27 courses/TSPL/2022/Instructions.tex
update exam instructions

\documentclass[12pt]{article}
\usepackage{a4,amssymb}
% \setlength{\oddsidemargin}{-1.5cm}
% \addtolength{\textwidth}{2cm}
% \addtolength{\textheight}{3cm}

@@

\begin{center}
\large Types and Semantics for Programming Languages
\end{center}

@@

\begin{enumerate}

@@

\item
  You may log into your computer as soon as you are ready to do so.

\item
  To download the exam paper, open a terminal window and type:
  \begin{center}
    \texttt{getpapers}
  \end{center}
  This will create a subdirectory \texttt{tspl-pe} in your home directory,
  containing the following files.
  \begin{center}
    \begin{tabular}{ll}
      \texttt{tspl-pe/papers/exam.pdf}                & the exam \\
      \texttt{tspl-pe/papers/instructions.pdf}        & these instructions \\
      \texttt{tspl-pe/templates/Exam.lagda}           & exam template to edit \\
      \texttt{tspl-pe/original\_templates/Exam.lagda} & backup of exam template
    \end{tabular}
  \end{center}
  The directories \texttt{tspl-pe/papers} and
  \texttt{tspl-pe/original\_templates}
  are read only, but you may read and write \texttt{tspl-pe/templates}.

\item
  To setup the Agda environment, open a second terminal window and type:
  \begin{center}
    \texttt{tspl-setup}
  \end{center}
  This will open a browser, with three tabs which contain the textbook
  \emph{Programming Language Foundations in Agda}, the documentation for the
  Agda standard library, and the documentation for Agda.  (The browser may
  also attempt to link to the internet, which brings up a tab labeled
  ``Problem loading page''; this is expected and not a problem.)

{\it (Note that internet access has been disabled.)}

\begin{center}
  \textbf{Do nothing further until the start of the exam is announced!}
\end{center}

\hfill \textit{Please Turn Over}
\newpage

\item When the start of the exam is announced, open the exam paper
\begin{center}
  \texttt{tspl-pe/papers/exam.pdf}
\end{center}
with the standard PDF viewer.

\item Change to the template directory
\begin{center}
  \texttt{cd tspl-pe/templates}
\end{center}
and edit the file
\begin{center}
  \texttt{Exam.lagda}
\end{center}
to include your answers, using Emacs or anything else suitable.
You are recommended to save your work on a regular basis.

\item Before submitting, make sure your file is processed by Agda
  correctly. Code which prevents the file from compiling should be
  made into comments. If you fail to solve part of a problem, you
  may get more credit if you indicate clearly which part you have
  not solved.

\item \emph{Please ensure before submission that the file}
  \texttt{Exam.lagda} \emph{contains your solutions to the exam.}  Submit
  your file using the command:
  \begin{center}
  \texttt{examsubmit Exam.lagda}
  \end{center}
  If you get an error, please check carefully that your file is called
  \texttt{Exam.lagda} and that you are in the same directory as this
  file. If you continue to have problems, please contact one of the
  invigilators.

Repeated submit commands are allowed, and will overwrite previous
submissions.  The last file submitted will be the one marked.

@@

\end{enumerate}

>>>>

\documentclass[12pt]{article}
\usepackage{a4,amssymb}
\usepackage{hyperref}

% \setlength{\oddsidemargin}{-1.5cm}
% \addtolength{\textwidth}{2cm}
% \addtolength{\textheight}{3cm}

@@

\begin{center}
\large Types and Semantics for Programming Languages \\
\Large Final Exam
\end{center}

@@

\begin{itemize}

@@

\item
  You are permitted to use your browser to access the following:
  \begin{quote}
    \url{plfa.inf.ed.ac.uk} -- the course textbook \\
    \url{agda.readthedocs.io/en/v2.6.2.2/} -- the Agda user manual
  \end{quote}
  You are also permitted to bring in two sides of A4 printed notes,
  covering whatever you find helpful. These may be inspected by the
  invigilator.

\item
  You are not permitted to bring in or access other materials during
  the exam. The only web pages you may browse during the exam are
  those above. The only files you may access are the file \texttt{Exam.lagda.md}
  and the parts of the standard library directly referenced by
  that file. The invigilator may see what materials you are accessing
  at any time.

\item
  Please ensure before submission that the file
  \texttt{Exam.lagda.md} contains your solutions to the exam.
  Submit using Gradescope as normal.

@@

\end{itemize}
